\documentclass[a4paper,10pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{fontawesome5}

% Define colors
\definecolor{headerblue}{RGB}{44, 62, 80}
\definecolor{linkblue}{RGB}{41, 128, 185}
\definecolor{sectiongray}{RGB}{160, 160, 160}

% Header and Footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[R]{\href{mailto:sibir9266@gmail.com}{\faEnvelope \ sibir9266@gmail.com} \hspace{1cm} \faPhone \ 8248214218}
\fancyfoot[C]{\thepage}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=linkblue,
    urlcolor=linkblue
}

% Section format
\titleformat{\section}{\large\bfseries\color{headerblue}}{}{0em}{\vspace{-0.5em}}[\titlerule]

\begin{document}

% Name and Title
\begin{center}
    {\Huge \textbf{Sibivendhan K}} \\
    \vspace{3pt}
    \textit{Innovative Problem Solver | Data Enthusiast | Aspiring Mathematician} \\
    \vspace{5pt}
    \href{http://www.linkedin.com/in/sibivendhan-k-a25018293}{\faLinkedin \ LinkedIn: www.linkedin.com/in/sibivendhan-k-a25018293} \hspace{0.5cm}
    \href{https://github.com/Sibi-bot}{\faGithub \ GitHub: github.com/Sibi-bot}
\end{center}

\vspace{0.5cm}

% Career Objective
\section*{Career Objective}
Dynamic and results-oriented professional with a strong foundation in mathematics, programming, and analytical problem-solving. Committed to leveraging technical expertise and innovative thinking to deliver impactful solutions and drive organizational success. Seeking opportunities to contribute to challenging projects in a collaborative and growth-focused environment.

% Education
\section*{Education}
\begin{itemize}[leftmargin=1.5cm]
    \item \textbf{PSG College of Arts \& Science, Coimbatore, Tamil Nadu} \\
    Pursuing M.Sc. in Mathematics \hfill 2023 -- 2025 \\
    \textit{Percentage (so far):} 75.2\%
    \item \textbf{Loyola College, Chennai, Tamil Nadu} \\
    B.Sc. in Mathematics \hfill 2020 -- 2023 \\
    \textit{First Class}, CGPA: 7.01/10
    \item \textbf{SRKV Gurukulam, Ulundurpet, Tamil Nadu} \\
    Higher Secondary Education \hfill 2019 -- 2020 \\
    Percentage: 70.8\%
    \item \textbf{SRKV Gurukulam, Ulundurpet, Tamil Nadu} \\
    Secondary Education \hfill 2017 -- 2018 \\
    Percentage: 78.2\%
\end{itemize}

% Technical Skills
\section*{Technical Skills}
\begin{itemize}[leftmargin=1.5cm]
    \item \textbf{Programming Languages:} CSS, HTML, Python, C
    \item \textbf{Tools:} MATLAB, LaTeX, Excel
    \item \textbf{Soft Skills:} Adaptability, Team player, Problem-solving
\end{itemize}

% Certifications
\section*{Certifications}
\begin{itemize}[leftmargin=1.5cm]
    \item Certificate in Programming Techniques, Bharathidasan University, February 2015
    \item Certificate in 2D Animation, Bharathidasan University, February 2017
    \item Certificate in Programming Numerical Methods using C and Python, April 2023
\end{itemize}

% Project
\section*{Key Project}
\textbf{Analyzing Diabetic Vulnerability to Emerging Viral Threats} \\
\textbf{Objective:} Predict diabetes risk and identify vulnerable age groups. \\
\textbf{Methodology:} Simple Additive Weighting (SAW) and Fuzzy TOPSIS. \\
\textbf{Technologies:} MATLAB, Python, LaTeX, Excel, Fuzzy Logic. \\
\textbf{Key Findings:} Identified age groups most at risk for diabetes and viral threats.

% Internship
\section*{Internship Experience}
\begin{itemize}[leftmargin=1.5cm]
    \item \textbf{Sundaram Home Finance Ltd, Chennai, Tamil Nadu} \\
    Intern Web Page Developer \hfill Dec 2022 -- Jan 2023 \\
    \textbf{Responsibilities:}
    \begin{itemize}[leftmargin=1cm]
        \item Developed responsive web pages using HTML and CSS.
        \item Collaborated with teams to improve design and functionality.
    \end{itemize}
\end{itemize}

% Co-Curricular
\section*{Workshops}
\begin{itemize}[leftmargin=1.5cm]
    \item Workshop on MATLAB for Scientific Computing \hfill Dec 2023
    \item Strive to Thrive: An Intensive Workshop for JAM \& GATE \hfill Jan 2024
\end{itemize}

% Extra-Curricular Activities
\section*{Leadership and Extra-Curricular Activities}
\begin{itemize}[leftmargin=1.5cm]
    \item Chairperson, Department of Mathematics \hfill 2024 -- 2025
    \item I\&E Coordinator, Department of Mathematics \hfill 2023 -- 2024
    \item Organized events for the Drama Club \hfill 2016 -- 2017
\end{itemize}

% Hobbies
\section*{Hobbies}
\begin{itemize}[leftmargin=1.5cm]
    \item \textbf{Chess:} Engage in strategic thinking and problem-solving, enhancing critical thinking skills.
    \item \textbf{Drawing:} Express creativity and attention to detail through various drawing techniques.
\end{itemize}

\end{document}
